\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/related_work.tex
revise on related work.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

>>>>

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitations compared with \tool: 
(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.
